ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
6th topic
little fix to compile

    \topic{odgi break, groom, chop \& unchop} \odgi\ pangenome graphs are dynamic structures in \odgi\.
    \cmd{odgi break} removes cycles in the graph, reducing its topology complexity. \cmd{odgi groom}
    removes spurious inverting links by exploring the graph from the orientation supported by most paths. \cmd{odgi chop}
    divides long nodes into shorter ones at a maximum requested size, simplifying downstream analysis.
    \cmd{odgi unchop} allows joining nodes that can be merged without changing the graph topology, nor the
    embedded sequences, obtaining an equivalent, but more compact, representation of the graph.

@@

    \topic{odgi position} in variation graphs the coordinates are provided by the embedded path sequences. Indeed, the node
    IDs are not meant to be stable. \cmd{odgi position} finds, translates, and liftovers graph and path positions between
    different graphs by exploiting their shared path sequences (Figure~2\vphantom{\ref{fig:2}}).

>>>>

    \topic{odgi break, groom, chop \& unchop} \odgi\ pangenome graphs are dynamic structures in ODGI.
    \cmd{odgi break} removes cycles in the graph, reducing its topology complexity. \cmd{odgi groom}
    removes spurious inverting links by exploring the graph from the orientation supported by most paths. \cmd{odgi chop}
    divides long nodes into shorter ones at a maximum requested size, simplifying downstream analysis.
    \cmd{odgi unchop} allows joining nodes that can be merged without changing the graph topology, nor the
    embedded sequences, obtaining an equivalent, but more compact, representation of the graph.

@@

    \topic{odgi position} embedded paths provide stable coordinates regardless of the graph in which they are.
    \cmd{odgi position} finds, translates, and liftovers graph and path positions between different graphs by
    exploiting their shared path sequences (Figure~2\vphantom{\ref{fig:2}}).
